A Method for the Spectroscopic Inference of Stellar Parameters

### 2014-08-21 tex/paper.tex
more hfd tools

We opt for the computationally expedient approach that employs a library of model spectra, 
$\flam(\{\vt_{\ast}\}^{\rm grid})$, where $\vt_{\ast} = [T_{\rm eff}, \,\, \log{g}, \,\, 
[{\rm Fe/H}]]$.  However, it is worth noting that the techniques developed here are applicable to 
{\it any} ``back-end" that generates a model spectrum.  In our adopted approach, the model 
spectrum for an arbitrary $\vt_{\ast}$ is interpolated from a spectral library, 
\begin{equation} \label{eqn:interp}
\flam(\{\vt_{\ast}\}^{\rm grid}) \leadsto \flam(\vt_{\ast}),
\end{equation}
where we assign the symbol $\leadsto$ as an interpolation operator.  The multi-dimensional 
interpolation in Eq.~\ref{eqn:interp} needs to be performed many times, so computational efficiency 
is critical.  In practice, a simple tri-linear interpolation is suitably fast, but introduces an 
undesirable level of inaccuracy (particularly in the [Fe/H] dimension).  The interpolation quality 
can be empirically estimated by performing the operation in Eq.~\ref{eqn:interp} across a 
$\{\vt_{\ast}\}^{\rm grid}$ grid point, and then comparing the interpolated spectrum with the 
corresponding library spectrum.  After an extensive exploration of such calculations 
\citep[see also][]{husser12}, we concluded that the best combination of speed and accuracy can be 
achieved by pre-computing a {\it refined} spectral library using a cubic spline interpolation with 
a $\{\vt_{\ast}\}^{\rm grid}$ spacing of [20\,K, 0.1\,dex, 0.1\,dex], and then performing 
tri-linear interpolation over that refined grid.  Overall, this interpolation
technique is found to be accurate within a few percent per full-resolution
model pixel and $\lesssim 1$\% once the spectrum is downsampled to the pixels of the detector. Ideally,
this pre-interpolation could be avoided if the spectral library was computed
over a refined grid (with a substantial up-front computational investment); but
for the time being, we can empirically propagate these interpolation
uncertainties into the likelihood calculations (as will be described in 
Section~\ref{subsec:likelihood}).

@@

\begin{figure*}[!htb]
\begin{center}
  \includegraphics[draft, width=2.5in]{figs/stellar_triangle_Kurucz.png}
  \caption{The posterior probability function of the stellar parameters for WASP-14, an F star, as explored by the MCMC Gibbs sampler. These stellar parameters are marginalized over the Chebyshev ($\cheb$) and noise parameters ($\cov$). Figure generated with \texttt{triangle.py} \citep{foreman-mackey14}.
}
\label{fig:stellar_posterior}
\end{center}
\end{figure*}

>>>>

We opt for the computationally expedient approach that employs a library of model spectra, 
$\flam(\{\vt_{\ast}\}^{\rm grid})$, where $\vt_{\ast} = [T_{\rm eff}, \,\, \log{g}, \,\, 
[{\rm Fe/H}]]$.  However, it is worth noting that the techniques developed here are applicable to 
{\it any} ``back-end" that generates a model spectrum.  In our adopted approach, the model 
spectrum for an arbitrary $\vt_{\ast}$ is interpolated from a spectral library, 
\begin{equation} \label{eqn:interp}
\flam(\{\vt_{\ast}\}^{\rm grid}) \leadsto \flam(\vt_{\ast}),
\end{equation}
where we assign the symbol $\leadsto$ as an interpolation operator.  The multi-dimensional 
interpolation in Eq.~\ref{eqn:interp} needs to be performed many times, so computational efficiency 
is critical.  In practice, a simple tri-linear interpolation is suitably fast, but introduces an 
undesirable level of inaccuracy (particularly in the [Fe/H] dimension).  The interpolation quality 
can be empirically estimated by performing the operation in Eq.~\ref{eqn:interp} across a 
$\{\vt_{\ast}\}^{\rm grid}$ grid point, and then comparing the interpolated spectrum with the 
corresponding library spectrum.  After an extensive exploration of such calculations 
\citep[see also][]{husser12}, we concluded that this interpolation
technique is found to be accurate within a few percent per full-resolution
model pixel and $\lesssim 1$\% once the spectrum is downsampled to the pixels of the detector. Ideally,
this pre-interpolation could be avoided if the spectral library was computed
over a refined grid (with a substantial up-front computational investment); but
for the time being, we can empirically propagate these interpolation
uncertainties into the likelihood calculations (as will be described in 
Section~\ref{subsec:likelihood}).

@@

\begin{figure*}[!htb]
\begin{center}
  \includegraphics[width=0.5\textwidth]{figs/kurucz_triangle.pdf}
  \caption{The posterior probability function of the stellar parameters for WASP-14, an F star, as explored by the MCMC Gibbs sampler. These stellar parameters are marginalized over the Chebyshev ($\cheb$) and noise parameters ($\cov$). Figure generated with \texttt{triangle.py} \citep{foreman-mackey14}.
}
\label{fig:stellar_posterior}
\end{center}
\end{figure*}
